### 2016-08-15 Theorem1_FP.tex
finished cleaning up Theorem 1

\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$\calS \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
%$\rho_2 \getsr Func(\univ, [m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

\fixme{Tom is here in rewriting the proof.}
Moving on $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$. Therefore, without loss of generality, it can be assumed that $A$ halts just after it finds the $r$ false positives, and outputs $\calZ$(of size $r$). Further, we can also assume that every point in $\calZ$ has already been queried to $\QryOracle$. This assumption can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. Hence, if $\game{4}(A)=1$, there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively as shown in \Cref{fig:D}. So,
\begin{align}
\nonumber \Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1} &= \Prob{\game{4}(A) = 1}\\
\mathrm{or} \nudge \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= \Prob{\game{4}(A) = 1}\label{eq:7}
\end{align}
Let $\calF$ be the event of getting a false positive in a classic Bloom filter. Since, $D$ is a non-adaptive adversary, for $r=1$, it exactly simulates the classic Bloom filter game. Also, as the elements of $\calI$ are randomly sampled from $[\{1,2,\ldots,q\}]^r$, the event of any query indexed by $\calI$ being a false positive is mutually independent of any other query indexed by the same set. Hence,
\begin{align}
\nonumber \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= [\Prob{\calF}]^r\\
&\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:8}
\end{align}
Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.\\
From \Cref{eq:7,eq:8},
\begin{equation}
\Prob{\game{4}(A)=1} \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:9}
\end{equation}
Using \Cref{eq:6} in \Cref{eq:9}
\begin{align}
\Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}} & \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\\
\Prob{\game{2}(A)=1} &\leq \dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r\label{eq:10}
\end{align}

@@

%\caption{PRF game}\label{fig:prf}
\begin{figure}
\centering
\fpage{0.45}{
\hpagess{0.4}{0.35}
{
$\experimentv{\ExpPRF{F}{B}}$\\
$K \getsr \calK $\\
$\rho \getsr Func(\univ,[m])$\\
$b \getsr \bits$\\
$b' \getsr B^\calO$\\
Ret $[b = b']$\\
}
{
$\oracle{\calO \smallskip(x)}$\\
if $ b = 1$ then\\
\nudge Ret $F_K(x)$\\
Ret $\rho(x)$\\
}
}
\caption{The PRF experiment for a function family $F \colon \calK
  \times \calX \to [m]$. }\label{fig:prf}
\end{figure}

@@

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.7}{
\hpagess{0.55}{0.4}
{
$\adversaryv{D^{\QryOracle, \calS}}$\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $r \gets \QryOracle(x)$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ$\\
\nudge Ret $\calZ$
}
{
\oracle{$\QryOracle(x)$}\\
 Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to~$k$\\
\nudge $v_i = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\end{figure}

From \Cref{eq:0,eq:10,eq:13} \\
\begin{align}
\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} &\leq  \AdvPRF{F}{B_1} +
\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{align}

>>>>

\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
%$\rho_2 \getsr Func(\univ, [m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
Run $A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

Recall that adversary~$A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.  We can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
Under these assumptions, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be the false positives; it simulates the~$\QryOracle$ by returning 1 on the guessed queries, and 0 otherwise; and it halts by outputting the set of guessed queries.  Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}$.

Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries are distinct and not elements of the original set~$S$, since we assume no pointless queries. Hence, so are the points $x_1,x_2,\ldots,x_r$ returned by~$D$.  Let $\calF_i$ be the event that~$x_i$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

To summarize, we have 
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed

@@

%\caption{PRF game}\label{fig:prf}
\begin{figure}
\centering
\fpage{0.45}{
\hpagess{0.4}{0.35}
{
$\experimentv{\ExpPRF{F}{B}}$\\
$K \getsr \calK $\\
$\rho \getsr \Func(\univ,[m])$\\
$b \getsr \bits$\\
$b' \getsr B^\calO$\\
Ret $[b = b']$\\
}
{
$\oracle{\calO \smallskip(x)}$\\
if $ b = 1$ then\\
\nudge Ret $F_K(x)$\\
Ret $\rho(x)$\\
}
}
\caption{The PRF experiment for a function family $F \colon \calK
  \times \calX \to [m]$. }\label{fig:prf}
\end{figure}

@@

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S)}$\\[4pt]
$c \gets 0$, $\calX \gets \emptyset$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge Ret $r$\\
When $A$ halts:\\
\nudge Ret $\calX$
}
\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\end{figure}
